Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2025-01-06 ms.qmd
Added in new code to add the overall estimates for traits and life stage category analysis. Added in a sentence for R1

Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (overall contrast: `mean(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))` 95\% CI: `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.025)` to `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.975)`, $p_{MCMC}$ = `r pmcmc(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))`), except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C). Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).

>>>>

Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (overall contrast: `r mean(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))` 95\% CI: `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.025)` to `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.975)`, $p_{MCMC}$ = `r pmcmc(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))`), except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C). Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
